---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SUSDeveloper

<!-- badges: start -->
<!-- badges: end -->

The goal of SUSDeveloper package is to provide package dcependencies and datasets to MSSI researchers. 

The packages dependencies currently included in the SUSDeveloper package are: \
\
  - cancensus \
  - dodgr \
  - osmdata \
  - reticulate \
  - spocc \

## Installation

<!-- You can install the released version of SUSDeveloper from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("MSSI")
``` -->

You can install the development version of SUSDeveloper from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("anooshpoorian/SUSDeveloper")
```

## Usage

You can begin using the package by displaying all the data available to you via the display_dataset_list() function, which will report all the datasets available to you through the package.

Additionally, in order to save data combinations and queries, you can use save objects to the cloud using the data_upload(obj, name) function. Anyone is then able to retrieve this object using the data_retrieve(name) function. 

You can also add any data you upload to the master dataset list through the update_datalist(name, description) function. 

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(MSSI)
## basic example code
```




